---
title: "Homework 6"
author: "Mingee Choi"
date: 12/1/2022
output: github_document
---

# Problem 2

Create city_state variable and binary variable indicating whether homicide is solved.

```{r}
samp = rnorm(100)
length(samp)
```

Omit certain cities and Tulsa, AL. Limit analysis for whom victim_race is white or black. Make sure victim_age is numeric.

```{r}
samp = rnorm(100)
length(samp)
```

Fit logistic regression with resolved vs unresolved as outcome and victim and age, sex, and race, as predictors.Save glm as R object.

```{r}
samp = rnorm(100)
length(samp)
```

 Apply broom: tidy to object and obtain estimate and confidence interval of adjusted OR for solving homicides comparing male to female victims, keeping all other variable fixed.
 
```{r}
samp = rnorm(100)
length(samp)
```

Run glm for each cities in dataset and extract adjusted OR and CI for solving homicides comparing male to female victims. 

```{r}
samp = rnorm(100)
length(samp)
```

Plot that shows estimated ORs and CIs for each city.
```{r}
samp = rnorm(100)
length(samp)
```


# Problem 3
